Consumption and resistance across states and HRRs

### 2017-03-01 states/resistance/state-report.Rmd
cosmetic

gram_negs = c('Escherichia coli', 'Klebsiella pneumoniae',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Klebisella oxytoca', 'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)
```

@@

```{r load_data}
consumption_groups = read_tsv('consumption_groups.tsv')
resistance_groups = read_tsv('resistance_groups.tsv')

@@

# Antibiogram data, with individual records
abg = read_tsv('../../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by='zipcode') %>%
  right_join(resistance_groups, by='drug') %>%
  filter(big %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible)

@@

I want to be able to filter the bug/drug combinations by whether they are coherent in the resistance data. Does the geography (state or HRR) actually have any effect on the

@@

```{r}
all_result %>%
  filter(place=='state', coherent, explanatory=='cpkp') %>%
  ggplot(aes(x=correlation, y=coherent.adj.p.value)) +
  geom_point() +
  geom_abline(yintercept=0.05, col='red') +
  scale_y_reverse() +
  theme_minimal()
```

>>>>

gram_negs = c('Escherichia coli', 'Klebsiella pneumoniae',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Klebisella oxytoca', 'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

consumption_groups = read_tsv('consumption_groups.tsv')
resistance_groups = read_tsv('resistance_groups.tsv')
```

@@

```{r load_data}

@@

# Antibiogram data, with individual records
abg = read_tsv('../../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by='zipcode') %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible)

# Keep only those bug/drug combinations that are in at least 20 states
abg %<>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>%
  filter(n >= 20) %>%
  left_join(abg, by=c('bug', 'drug_group'))

@@

To ensure coherence, I only use the bug/drug combinations that appear in antibiograms in at least 20 states. This is equivalent to filtering those bug/drug combinations that have at least 125 records.

@@

```{r}
all_result %>%
  filter(place=='state', coherent, explanatory=='cpkp') %>%
  ggplot(aes(x=correlation, y=coherent.adj.p.value)) +
  geom_point() +
  geom_hline(yintercept=0.05, col='red') +
  scale_y_reverse() +
  theme_minimal()
```
